---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# TestFunctions

[![Travis-CI Build Status](https://travis-ci.org/CollinErickson/TestFunctions.svg?branch=master)](https://travis-ci.org/CollinErickson/TestFunctions)

## Why should I use it?

This R package provides functions for various surfaces that can be used 
for testing of models, algorithms, etc. For example, if you want to compare
how well a neural network does compared to a random forest, you can take 
data from one of these test functions to train and test them. 

## How do I use it?

Each of the test functions is called like any other function. The first argument, `x`, should
be a vector representing one point or a matrix that has points in its rows. This can cause 
problems if you are using a 1-dimensional function and pass in a vector of values. 
Instead you should pass them in as a matrix with a single column, or vectorize the function.

```{r}
library(TestFunctions)
branin(runif(2))
branin(matrix(runif(20), ncol=2))
```

```{r}
cf::cf(banana)
```


## How do I get it?

Install it like any other package with `install.packages`.
