---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```


# TestFunctions

<!-- badges: start -->
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/TestFunctions)](https://cran.r-project.org/package=TestFunctions)
[![codecov](https://codecov.io/github/CollinErickson/TestFunctions/graph/badge.svg?token=FMnP9TEFBk)](https://codecov.io/github/CollinErickson/TestFunctions)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/last-month/TestFunctions?color=blue)](https://r-pkg.org/pkg/TestFunctions)
[![R-CMD-check](https://github.com/CollinErickson/TestFunctions/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CollinErickson/TestFunctions/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Why should I use it?

This R package provides functions for various surfaces that can be used 
for testing of models, algorithms, etc. For example, if you want to compare
how well a neural network does compared to a random forest, you can take 
data from one of these test functions to train and test them. 

## How do I use it?

Each of the test functions is called like any other function. The first argument, `x`, should
be a vector representing one point or a matrix that has points in its rows. This can cause 
problems if you are using a 1-dimensional function and pass in a vector of values. 
Instead you should pass them in as a matrix with a single column, or vectorize the function.

```{r}
set.seed(0)
library(TestFunctions)
branin(runif(2))
branin(matrix(runif(20), ncol=2))
```

```{r bananacont}
ContourFunctions::cf(banana)
```


## How do I get it?

Install it like any other package with `install.packages`.

```
install.packages("TestFunctions")

# Or the the development version from GitHub:
# install.packages("devtools")
devtools::install_github("CollinErickson/TestFunctions")
```
